First and foremost, I would like to thank my advisor and mentor, Dr.~Alan Wuosmaa for giving me the opportunity to work on this project.  In the nearly seven years that I have had the privilege of working with Dr.~Wuosmaa, he has never been too busy to answer a question and I thank him greatly for sharing with me his 
knowledge and expertise.  Were it not for his painstaking support, this dissertation, nor the article that preceded it, would have been possible.

I would like to thank Dr.~Birger Back who has been my supervisor at Argonne National Laboratory for the past four years.  His continued support and guidance have been invaluable throughout the course of this work.  I would also like to thank Dr.~Dean Halderson and Dr.~Kirk Korista for agreeing to be on my dissertation committee, and for their help and guidance.

I would like to %thank and 
acknowledge the tireless efforts of two of my colleagues from Western Michigan University, Scott Marley and Jack Winkelbauer.  Their countless hours of hard work over the years, on this project and others, have made them not only indispensable collaborators, but valued friends.  Thank you both.

Finally, I would like to thank %my family, specifically 
my parents and my grandfather for their unwavering support which has made them behind-the-scenes partners in this work.  The bulk of the writing of this dissertation was fueled by cookies, sandwiches, and other delicious food, made with love by my wife, whom I met during the course of this work (which is perhaps the most surprising outcome of being involved with this project); many thanks to her.

As far back as I can remember, I have always been interested in physics.  It was my grandfather, the late Dr.~James Cockrell, that first showed me the allure that physics holds.  This dissertation is dedicated to him.



This work was supported by the U.\ S. Department of Energy,
Office of Nuclear Physics, under contracts N$^\textrm{o}$~DE-FG02-04ER41320 (WMU) 
and N$^\textrm{o}$~DE-AC02-06CH11357 (ANL); and by the National Science Foundation, grants N$^\textrm{o}$~PHY-02-16783  (JINA) and N$^\textrm{o}$~PHY-07-58099 (MSU). 