\chapter{Publication History}
\section{Article}
\label{fig_notes}
The bulk of the material discussed in this dissertation was originally published by the author and collaborators in Ref.~\cite{Lighthall_2010}.  Each of the figures from this reference appear in this dissertation with the modifications listed below.
\renewcommand{\arraystretch}{1.3} % set array line spacing
\begin{table*}[ht]%
  \centering
  \begin{tabular}{lll}
    \hline
    Ref.~\cite{Lighthall_2010}&Current&Modifications\\
    \hline \hline
    Fig.~1&Fig.~\ref{schematic}&none; same file\\
    Fig.~2&Fig.~\ref{analytic}&panels c) and d) are added\\
    Fig.~3&Fig.~\ref{map}&$\rho=45$\,cm is added, only measured points are shown\\
    Fig.~4&Fig.~\ref{solenoid}&none; same file\\
    Fig.~5&Fig.~\ref{psd_test}&threshold cutoff is plotted\\
    Fig.~6&Fig.~\ref{psd_energy}&``counts per'' units added\\
    Fig.~7&Fig.~\ref{psd_pos}&ROOT histograms are used in place of grace plots\\
    Fig.~8&Fig.~\ref{pcb}&none; same file\\
    Fig.~9&Fig.~\ref{array_pic}&none; same file\\
    Fig.~10&Fig.~\ref{sim_plots}&none; same file\\
    Fig.~11&Fig.~\ref{hTOF}&``counts per'' units added\\
    Fig.~12&Fig.~\ref{cezg_350}&none; same file\\
    Fig.~13&Fig.~\ref{hEZ}&acceptance cutoff is labeled\\
    Fig.~14&Fig.~\ref{double}&acceptance cutoffs are plotted\\
    Fig.~15&Fig.~\ref{qval}&$x$-scale expanded, states labeled\\
    Fig.~16&Fig.~\ref{angdist2}&figure in two panels, data from Ref.~\cite{Mermaz_1971} plotted\\
    \hline
  \end{tabular}
  \caption[Comparison of reproduced figures.]{Comparison of reproduced figures.  Each of the 16 figures in Ref.~\cite{Lighthall_2010} appear in some form in this document.}
  \label{fig_corr}
\end{table*}

\section{Drafts}
Table~\ref{history_table} shows the revision history of this document. Each official draft was defined by having been submitted for review. Appendix \ref{changes} is an exhaustive list of changes made to this document between June 2011, after being accepted by the Western Michigan University Graduate College, and September 2019, when the content of this document was place under version control in a GitHub repository\cite{Lighthall_thesis_2021}.
\begin{table}[ht]%
 \mmddyydate % set date format
\renewcommand{\arraystretch}{1.3} % set array line spacing
\centering
\begin{tabular}{ccllll}
% Revision History ------------%-------------------------------
\hline
Draft&Format&Date&Submitted to&Chapters&Comments\\ \hline \hline
0 &.tex&  \formatdate{15}{02}{09} &---&---&created\\
1 &.pdf&  \formatdate{24}{08}{10} & AHW& all\\
2 &.pdf&  \formatdate{19}{11}{10} & AHW& 7\\
3 &.pdf&  \formatdate{14}{12}{10} & AHW& 5,7\\ 
4 &.pdf&  \formatdate{02}{02}{10} & AHW& 5,7 \\
5 &.pdf&  \formatdate{20}{02}{10} & AHW& 9 \\
6 &.pdf&  \formatdate{14}{03}{10} & AHW& 14\\
7 &.pdf&  \formatdate{22}{03}{10} & AHW& 10\\
8 &.pdf&  \formatdate{30}{03}{10} & AHW& 12\\
9 &.pdf&  \formatdate{03}{04}{10} & AHW& 11\\
10 &.pdf&  \formatdate{05}{04}{10} & AHW& 16\\
11 &.pdf&  \formatdate{22}{04}{10} & AHW& all\\
12 &.pdf&  \formatdate{24}{04}{10} & AHW& 10,12,14\\
13 &.pdf&  \formatdate{28}{04}{10} & AHW, BBB, DH, KK &all\\
14 &.pdf&  \formatdate{30}{04}{10} & AHW, BBB, DH, KK& all&approved\\
15 &.pdf&  \formatdate{27}{05}{10} & JWH&all\\
16 &.pdf&  \formatdate{15}{06}{10} & JWH &all&accepted\\
17 &.pdf&  \formatdate{04}{09}{19} & & all & Overleaf, GitHub\\ \hline
\end{tabular}
\caption[Revision history.]{Revision history. The file format and completion date of each revision is given.  The content of each draft is listed including who the draft was submitted to.}
\label{history_table}
\end{table}

\section{Publication}
\subsection{Print}
This document was originally published by UMI Dissertation Publishing, a division of ProQuest \cite{Lighthall_2011}. UMI 3471048. ISBN 9781249838647. 170 pages; 173 with publisher's . Approximately 64,000 words.

\subsection{Digital}
\subsubsection{Paid}
\noindent\url{https://dissexpress.proquest.com/dxweb/results.html?&pubnum=3471048}\\
\noindent\url{https://www.proquest.com/openview/4067b3246bd2af115fb1585b4aad75cb/1}
\subsubsection{Open}
\noindent\url{https://scholarworks.wmich.edu/dissertations/432/}\\
Recommended Citation
\begin{quote}
Lighthall, Jonathan C., "Commissioning of the Helical Orbit Spectrometer: A New Device for Measuring Nuclear Reactions in Inverse Kinematics" (2011). Dissertations. 432.\\
\url{https://scholarworks.wmich.edu/dissertations/432}
\end{quote}

\subsection{Copyright}
The author is copyright holder of the original published work, registration number TX0006735169, effective October 31, 2011.

\section{Development}
The appendices beyond Appendix~\ref{field_map_data} have been added since publication.
Appendix~\ref{changes} lists the changes made to this document since publication.
Appendix~\ref{runs} lists the HELIOS experiments during the author's tenure at ANL.
Appendix~\ref{sim_man} contains the manual for the simulations referred to in Chapt.~\ref{simulation}.
Appendix \ref{badang} is a discussion of the analysis methods used in \cite{Schiffer_2010}.

Since September, 2019, the code that produces the contents of this document have been under version control using Git. The Git repository is hosted on GitHub and carries its own copyright \cite{Lighthall_thesis_2021}. The repository contains over 44,000 lines of code.

\section{Citations}
The published work has been cited by the following publications.
\begin{enumerate}
    \item Development of Novel Scintillation Detection Techniques for Use in Nuclear Physics and Medical Applications
    \item A direct study of $^{20}$Ne($\alpha$,$p$)$^{23}$Na with the HELIcal Orbit Spectrometer (HELIOS)
\end{enumerate}